## Exercise 4: Armed Conflicts, Visualization and Fact Checking

### Introduction

For the second homework we will use data from [ACLED - Armed Conflict Location & Event Data Project (ACLED)](https://www.acleddata.com/about-acled/). 

> The ACLED project codes reported information on the type, agents, exact location, date,
and other characteristics of political violence events, demonstrations and select
politically relevant non-violent events. ACLED focuses on tracking a range of violent and
non-violent actions by political agents, including governments, rebels, militias,
communal groups, political parties, external actors, rioters, protesters and civilians. Data
contain specific information on the date, location, group names, interaction type, event
type, reported fatalities and contextual notes. 


You are provided with two datasets:
  
* __events_data__ - news reports of armed conflicts with detailed information about each event.
* __region_data__ - information about the locations appearing in `events_data` and the corresponding country and region.

```{r}
event_data <- read_csv(here("data/event_data.csv"))
region_data <- read_csv(here("data/region_data.csv"))
```

### Wrangling and visualization


__1.a__ From the dataset `event_data`, you will use only:
  
* `event_id_cnty` - unique event identifier
* `event_date` - date when the event happened
* `event_type` - type of the conflict 
* `actor1` - first party associated with the conflict
* `actor2` - second party associated with the conflict
* `country` - name of the country where the event happened 
* `location` - name of the location where the event happened
* `source` - what was the source of the report for the event
* `source_scale` -  whether the source for most information is at the local, regional, national or international level
* `notes` - additional contextual important details
* `fatalities` - number of reported fatalities related to the event

Modify `event_data` to select only the variables mentioned above.

```{r}
## Your code goes here
```

__1.b__ Use `lubridate`'s `dmy` function to transform `event_date` to a **"YYYY - MM - DD" format**. What is the time period covered by this dataset? 

```{r}
## Your code goes here
```

__1.c__ How many countries are mentioned in the dataset? Which one has the highest number of armed conflicts? Create a barplot with the number of conflicts per country? 
(Hint: use `reorder` so that the counts are displayed in an orderly fashion.) 
Interpret the figure.

```{r}
## Your code goes here
```

__1.d__ To complete the information in `event_data`, add a column `region` using the data from `region_data`. The unique combination you can use for a join is `c("country","location")`. What will happen if you join the datasets by `location`?

```{r}
## Your code goes here
```


__1.e__ Add two new columns to `event_data` for the __month__ and __year__, extracted from `event_date`. Create a line plot that displays the number of monthly conflicts per month for each year 2015 to 2017. Do you notice a specific year with particularly high number of conflicts?  


```{r}
## Your code goes here
```
__1.f__ Create another line plot  of the number of conflicts for each month **per country**. What can you notice? Can you relate the plot to recent worldwide events?

```{r}
## Your code goes here
```

### Fact checking 

Nigeria's President Muhammadu Buhari has repeatedly said that the Boko Haram jihadist group had been defeated, but [this article from BBC analysis of Boko Haram attacks](http://www.bbc.com/news/world-africa-42735414) shows that little has changed. With the data that you already have, you can do the fact checking yourself. 

__1.g__ From `event_data` filter only the conflicts based in Nigeria, and only the ones where Boko Haram appears as `actor1` or `actor2`. Print the number of fatalities per year resulting from those conflicts. Has the number of fatalities gone down in 2016 and 2017 compared to 2015 as president Buhari is stating?
  
```{r}
## Your code goes here
```


__1.h__ Another interesting fact mentioned in the BBC article is that the coverage of conflicts in Western Africa is limited especially at the level of **local** sources. To investigate this claim, produce a barplot for the number of news reports (conflicts) coming from different `source_scale`, namely "International", "National" and "Local" by region. 
(Hint: use `fct_reorder` and `fill` to produce a data to chart ratio as high as possible.)
Is the statement about limited local reporting in Western Africa supported by this graph?
  
```{r}
## Your code goes here
```


