## Exercise 2: Motor Trend Car Road Tests

In this exercise, you will use the `mtcars` dataset from the `datasets` package. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

__2.a__ Load the dataset mtcars. How many observations and variables does this dataset have?

```{r}
# your code goes here
```

__2.b__ Print out the mtcars data frame sorted by hp (descending order).

```{r}
# your code goes here
```

__2.c__ Create a new object named `cars_cyl` and assign to it the `mtcars` data frame grouped by the number of cylinders.

```{r}
# your code goes here
```

__2.d__ Modify `cars_cyl` to remove all variables except the average miles/(US) gallon and gross horsepower for each cylinder group.

```{r}
# your code goes here
```

__2.e__ Print out the average miles/(US) gallon and gross horsepower for each cylinder group.
What can you conclude about the effect of the number of cylinders on the other two variables?

```{r}
# your code goes here
```

__2.f__ Improve the summary statistics by also displaying the median, the minimum, the maximum, the standard deviation and the count.

```{r}
# your code goes here
```

__2.g__ Modify `cars_cyl` by adding a new variable called `perf = hp/mpg` and another
variable `rank` indicating the rank of the cars in terms of performance (the higher the better). 
Print out the resulting table by decreasing performance.

```{r}
# your code goes here
```

__2.h__ Print out the average performance for each 
number of cylinders. What can you say about the relationship between the two variables?

```{r}
# your code goes here
```

__2.i__ Using the full dataset, plot the relationship between the weight and miles per US gallon, with a different color for each number of cylinder. What can you conclude about the relationships between the three variables? Bonus: add a (linear) regression line for each group.

```{r}
# your code goes here
```

__2.j__ Using the full dataset, plot the performance (gross horsepower divided by miles per US gallon) as a function of the weight, with a different color for each number of cylinders and a different shape for each type of transmission. What can you conclude about the relationships 
between the four variables?

```{r}
# your code goes here
```

__2.k__ Save `cars_cyl` as a `.csv` into the `results` subdirectory in your project.

```{r}
# your code goes here
```

