## Exercise 2: Motor Trend Car Road Tests

In this exercise, you will use the `mtcars` dataset from the `datasets` package. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

__2.a__ Load the dataset mtcars. How many observations and variables does this dataset have?

```{r}
library(datasets)
mtcars<-datasets::mtcars
```

__2.b__ Print out the mtcars data frame sorted by hp (descending order).

```{r}
mtcars%>%arrange(desc(hp))
```

__2.c__ Create a new object named `cars_cyl` and assign to it the `mtcars` data frame grouped by the number of cylinders.

```{r}
cars_cyl <- mtcars %>% group_by(cyl) %>% arrange(cyl)
```

__2.d__ Modify `cars_cyl` to remove all variables except the average miles/(US) gallon and gross horsepower for each cylinder group.

```{r}
cars_cyl <-  cars_cyl %>% group_by(cyl) %>%  select(cyl, hp, mpg) 
```

__2.e__ Print out the average miles/(US) gallon and gross horsepower for each cylinder group.
What can you conclude about the effect of the number of cylinders on the other two variables?

```{r}
cars_cyl%>% select(mpg,hp,cyl)%>%print
#We can observe a negative correlation between the variables mpg and cyl. In the other hand, we observe a positive correlation between the variables hp and cyl
```

__2.f__ Improve the summary statistics by also displaying the median, the minimum, the maximum, the standard deviation and the count.

```{r}
summarise(cars_number=n(),
           cars_cyl, mean(hp), median(hp), min(hp), 
           max(hp), sd(hp), mean(mpg), median(mpg), 
           min(mpg), max(mpg), sd(hp))
```

__2.g__ Modify `cars_cyl` by adding a new variable called `perf = hp/mpg` and another
variable `rank` indicating the rank of the cars in terms of performance (the higher the better). 
Print out the resulting table by decreasing performance.

```{r}
cars_cyl<-cars_cyl %>% mutate( perf = hp/mpg, rank=rank(-perf)) %>% arrange(desc(perf))

print(cars_cyl)
```

__2.h__ Print out the average performance for each 
number of cylinders. What can you say about the relationship between the two variables?

```{r}
cars_cyl %>% summarise(avg_perf = mean(perf))
#The relationship between the two variables is (positively) exponential
```

__2.i__ Using the full dataset, plot the relationship between the weight and miles per US gallon, with a different color for each number of cylinder. What can you conclude about the relationships between the three variables? Bonus: add a (linear) regression line for each group.

```{r}
ggplot(mtcars, aes(wt,mpg))+ 
  geom_jitter(height = 2, width = 2, color=mtcars$cyl) + 
  geom_smooth(method = lm, se=FALSE, mapping=aes(group=mtcars$cyl))

# We observe a negative relationship between mpg and wt. No specific relationship between cyl and wt. Finally, We observe a positive relationship between mpg and cyl
```

__2.j__ Using the full dataset, plot the performance (gross horsepower divided by miles per US gallon) as a function of the weight, with a different color for each number of cylinders and a different shape for each type of transmission. What can you conclude about the relationships 
between the four variables?

```{r}
ggplot(mutate(mtcars, perf = hp/mpg), mapping=aes(mpg,perf)) + geom_point(height = 2, width = 2, color=mtcars$cyl, shape=mtcars$am) 
```

__2.k__ Save `cars_cyl` as a `.csv` into the `results` subdirectory in your project.

```{r}
# your code goes here
```

